---
title: "Shiny Application"
date: "09/06/2020"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Coronavirus (COVID-19) Cases

The COVID-19 pandemic in India is part of the worldwide pandemic of coronavirus disease 2019 (COVID-19) caused by severe acute respiratory syndrome coronavirus 2(SARS-CoV-2) .The first case of COVID-19 in India, which originated from China, was reported on 30 January 2020. As of 9 June 2020, the MoH&FW has confirmed a total of 266,598 cases, 129,215 recoveries (including 1 migration) and 7,466 deaths in the country.
India currently has the largest number of confirmed cases in Asia,with the number of total confirmed cases breaching the 100,000 mark on 19 May and 200,000 on 3 June.


## points plot on X-axis

- date
- median_age

## points plot on Y-axis

- total_case
- new_case
- total_death
- new_death
- covid_death_rate


## Interactive Plot

```{r Covid}
 titlePanel("Cases of Covid-19") 
     sidebarLayout(     
         sidebarPanel(
         #input using radiobuttons 
             radioButtons("C", "Select Country:",                    
                          list("India"="India"),width = "200px"
                          ),
              radioButtons("X", "Select X-axis:",                    
                          list( "date"='b', "median_age"='e'
                               ),width = "400px"
                          ),
              radioButtons("Y", "Select Y-axis:",                    
                           list( "total_case"='f', "new_case"='g',
                                "total_death"='h', "new_death"='i',"cvd_death_rate"='j'
                           ),width = "400px"
            ),
        ),   
    # Show a plot of the generated distribution       
    mainPanel( 
             plotOutput("distPlot") 
             )     
    )   

output$distPlot<-renderPlot({ 
        #creating distPlot  
        if(input$X=='b') { i<-2 }    
        if(input$X=='e') { i<-5 }     
        if(input$Y=='f') { j<-6 }     
        if(input$Y=='g') { j<-7 }     
        if(input$Y=='h') { j<-8 }     
        if(input$Y=='i') { j<-9 }   
        if(input$Y=='j') {j<-10}

        #reading covid cases dataset    
        library(dplyr)
        library(graphics)
        covid<-read.csv("D:/Data Science/Shiny Project/owid-covid-data.csv")  
        result<-data.frame(filter(group_by(covid,location),location==input$C))
        result_without_NA<-na.omit(result)
        if(i==2){
            X    <- as.Date(result_without_NA$date)
        }
        else{
            X <-result_without_NA$median_age
        }
           
        Y    <- result_without_NA[,j]
        #Calculate the range of X
        rangex<-range(X)
        #calculate tthe range of Y
        rangey<-range(Y)
        #set the xlim and ylim of a plot
        plot.window(rangex,rangey)
        #draw a plot 
        plot(X,Y,pch=20,col="red",xlab = ,main ="Covid case in India")

        }) 
       
```




